The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth

### 2021-09-28 paper/paper.Rmd
Edit the bullet point in conclusion based on isse #8.

- determining which records should be downloaded from the database.
- there are many errors in the data, e.g. hourly wages greater than $30,000 per hour, and there was no information on how these were handled in the original data.
- there is no explicit variable in the database recording high school dropout, which means we needed to compare date of 12th grade with the individual's age.
- calculating experience in the workforce, would require knowing the time of first job within the first year the individual was recorded.

@@

- **Codes** : R script to reproduce data tidying and cleaning are available in this [Github Repository](https://github.com/numbats/yowie/blob/master/data-raw/data_preprocessing.R).

@@

- **shiny app**: An web interactive `shiny` app to run a simulation to customize the weight threshold. This app could be accessed [here](https://github.com/numbats/wages-refresh/tree/main/app).

>>>>

- determining which records should be downloaded from the database.
- there are many errors in the data, e.g. hourly wages greater than $30,000 per hour. Further for original data, wages greater than 75 dollars were set to be missing. However, in recent context, this value might be too low to be set as the maximum threshold. 
- there is no explicit variable in the database recording high school dropout, which means we needed to compare date of 12th grade with the individual's age.
- calculating experience in the workforce, would require knowing the time of first job within the first year the individual was recorded.

@@

- **Codes** : R script to reproduce data tidying and cleaning are available in this [page](https://numbats.github.io/yowie/articles/process-data.html).

@@

- **shiny app**: An web interactive `shiny` app to customize the weight threshold. This app could be accessed [here](https://github.com/numbats/wages-refresh/tree/main/app).
